The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-07-01 exp-resurgence.tex
Finish opening paragraph of Airy thimble projection reasoning

Through a similar calculation, we see that $\borel\big[ e^z z^{-1/2}\,\tilde{W}_{-1} \big]$ sums to
\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_{-1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big). \]
Looking back at Section~\ref{neg-root-AL}, we recognize this as a scalar multiple of $v_{-1}$.
%
\subsubsection{Thimble projection reasoning}\label{contour-argument-AL}
We can also study the Airy-Lucas functions by applying the thimble projection formula to integral~\eqref{integral:mod-bessel-rational-AL}, specializing the reasoning behind Lemma~\ref{lem:thimble_proj_formula-proof}. We recast integral~\eqref{integral:mod-bessel-rational-AL} into the $\zeta$ plane by setting $-\zeta = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$. Recall from below equation~\eqref{integral:AL} that the integration contour $\mathcal{C}^\theta_j$ run through the critical point $u = \cos\big(\tfrac{j}{n}\pi\big)$, with its direction determined by the parameter $\theta$. The critical point splits $\mathcal{C}^\theta_j$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away. Recalling that $\mathcal{C}^\theta_j$ is a preimage of $\mathcal{J}^\theta_{\zeta, \mp 1}$, we get
\begin{align*}%%\label{integral:mod-bessel-rational-zeta}
K^{(j)}_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
& = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right]
\end{align*}
where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $\mathcal{C}^\theta_j$, respectively. \begin{todo}[Draw the thimble in the $u$ plane?]\end{todo}

@@

\subsection{Specializing from the Airy--Lucas examples \begin{todo}[improve title]\end{todo}}

@@

\begin{equation}\label{integral:mod-bessel}

@@

Let us find a germ in $(\zeta+1)^{\tau_{-1}-1}\,\mathcal{O}_{\zeta=-1}$, for some $\tau_{-1} \in (0, 1)$, that satisfies equation~\eqref{diff-eq:spatial-mod-bessel-AL}. In the rescaled coordinate from Section~\ref{pos-root-AL}, this is the point $\xi_1 = 1$. Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} that represents a germ in $(1-\xi_1)^{-1/2}\,\mathcal{O}_{\xi_1=1}$:
v_{-1} &=\;& (1-\xi_1)^{-1/2} &\;{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; 1-\xi_1\big) \\[1mm]
&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} &\;{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big),
where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$. By the same reasoning as before, $v_{-1}$ is holomorphic throughout the sector $\Omega_{-1} = \C \smallsetminus \mathcal{J}^0_{\zeta_{-1}, 0}$, and it belongs to the space
for all $\Lambda > 0$. It has a well-defined Laplace transform along any ray from $\zeta = -1$ except the one going directly right, and its Laplace transform can be written as

@@

Through a similar calculation, we see that $\borel\big[ e^z z^{-1/2}\,\tilde{W}_{-1} \big]$ sums to
\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_{-1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big). \]
Looking back at Section~\ref{neg-root}, we recognize this as a scalar multiple of $v_{-1}$.

\end{revised}
\begin{old}
Just as in Section~\ref{confirmation-borel-regularity}, we compute
\begin{align*}
\borel_\zeta \big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big] & = \borel_\zeta \left[ e^{-z} \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k-\frac{1}{2}} \right] \\
& = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{k!} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^{k-\frac{1}{2}}}{\Gamma\big(k+\frac{1}{2}\big)} \\
& = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{k!} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^{k-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big) \left(\frac{1}{2}\right)_k} \\
& = \frac{\zeta_1^{-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big)} \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{\left(\frac{1}{2}\right)_k} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^k}{k!},
\end{align*}
we see that $\borel\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big]$ sums to
\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_1^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
Looking back at Section~\ref{pos-root-AL}, we recognize this as a scalar multiple of $v_1$.

Through a similar calculation, we see that $\borel\big[ e^z z^{-1/2}\,\tilde{W}_{-1} \big]$ sums to
\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_{-1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big). \]
Looking back at Section~\ref{neg-root-AL}, we recognize this as a scalar multiple of $v_{-1}$.
\end{old}
%
\subsubsection{Thimble projection reasoning}\label{contour-argument-airy}
\begin{revised}
In Section~\ref{contour-argument-AL}, we specialized the reasoning behind Lemma~\ref{lem:thimble_proj_formula-proof} to the case of the Airy--Lucas functions. We now specialize even further, down to the case of the Airy function. \begin{todo}[\ldots]\end{todo}
\begin{align*}
K(z) & = \begin{todo}-\end{todo}i\sqrt{3} \int_{\mathcal{C}^\theta_1} \exp\left[z \left(4u^3 - 3u\right)\right]\,du \\
& = \frac{i}{\sqrt{3}} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{1}{4u_+^2 - 1}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{1}{4u_-^2 - 1}\,d\zeta \right]
%% & = \frac{i}{\sqrt{3}} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} \frac{e^{-z\zeta}\,d\zeta}{4u_+^2 - 1} - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} \frac{e^{-z\zeta}\,d\zeta}{4u_-^2 - 1} \right]
\end{align*}
\begin{verify}
\begin{align*}%%\label{integral:mod-bessel-rational-zeta}
K(z) & = \frac{3}{2 \sinh\big(\tfrac{1}{3}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
& = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right]
\end{align*}
\end{verify}
Recognizing $4u^3 - 3u$ as the Chebyshev polynomial $T_3(u)$, we introduce a new variable $\phi$ with $u = \cos(\phi)$ and $-\zeta = \cos(3\phi)$. On the $\phi$ plane, which is an infinite branched cover of the $u$ plane, we can lift $\mathcal{C}^\theta_1$ to the path $\tfrac{\pi}{3} + i\R$. The incoming and outgoing branches lift to $\tfrac{\pi}{3} - i[0, \infty)$ and $\tfrac{\pi}{3} + i[0, \infty)$, respectively. \begin{todo}[Draw the lifted thimble in the $\phi$ plane?]\end{todo}

@@

In the projected thimble integral
\[ K(z) = \frac{i}{\sqrt{3}} \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\left[\frac{1}{4u_+^2 - 1} - \frac{1}{4u_-^2 - 1}\right]\,d\zeta, \]
we can now see the integrand as the variation of the function
\[ \frac{1}{4\cos(\phi)^2 - 1} = \frac{1}{2}\;{}_2F_1\left(\frac{2}{3},\;\frac{4}{3};\;\frac{3}{2};\frac{1}{2} - \frac{\zeta}{2}\right) + \frac{1}{6}\;{}_2F_1\left(\frac{2}{3},\;\frac{4}{3};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) \]
across the branch cut $\mathcal{J}^\theta_{\zeta,1}$. The first term is regular at $\zeta = 1$, so only the second term contributes to the jump. We can write the jump explicitly using identity~15.2.3 from \cite{dlmf}:
\[ K(z) = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{6},\;\frac{5}{6};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta. \]
Comparing this expression with the expression for $V_1$ in Section~\ref{pos-root}, we see that
\[ K(z) = \tfrac{i}{2}\laplace_{\zeta, 1} v_1. \]
\end{revised}
\begin{old}\par
We can also study the Airy-Lucas functions by applying the thimble projection formula to integral~\eqref{integral:mod-bessel-rational-AL}, specializing the reasoning behind Lemma~\ref{lem:thimble_proj_formula-proof}. We recast integral~\eqref{integral:mod-bessel-rational-AL} into the $\zeta$ plane by setting $-\zeta = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$. Recall from below equation~\eqref{integral:AL} that the integration contour $\mathcal{C}^\theta_j$ run through the critical point $u = \cos\big(\tfrac{j}{n}\pi\big)$, with its direction determined by the parameter $\theta$. The critical point splits $\mathcal{C}^\theta_j$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away. Recalling that $\mathcal{C}^\theta_j$ is a preimage of $\mathcal{J}^\theta_{\zeta, \mp 1}$, we get
\begin{align*}%%\label{integral:mod-bessel-rational-zeta}
K^{(j)}_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
& = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right]
\end{align*}
where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $\mathcal{C}^\theta_j$, respectively. \begin{todo}[Draw the thimble in the $u$ plane?]\end{todo}

@@

\begin{equation}\label{integral:mod-bessel}

>>>>

Through a similar calculation, we see that $\borel\big[ e^z z^{-1/2}\,\tilde{W}_{-1} \big]$ sums to
\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_{-1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big). \]
Looking back at Section~\ref{neg-root-AL}, we recognize this as a scalar multiple of $v_{-1}$.
%
\subsubsection{Thimble projection reasoning}\label{contour-argument-AL}
We can also study the Airy-Lucas functions by applying the thimble projection formula to integral~\eqref{integral:mod-bessel-rational-AL}, specializing the reasoning behind Lemma~\ref{lem:thimble_proj_formula-proof}. We recast integral~\eqref{integral:mod-bessel-rational-AL} into the $\zeta$ plane by setting $-\zeta = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$. Recall from below equation~\eqref{integral:AL} that the integration contour $\mathcal{C}^\theta_j$ runs through the critical point $u = \cos\big(\tfrac{j}{n}\pi\big)$, with its direction determined by the parameter $\theta$. The critical point splits $\mathcal{C}^\theta_j$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away. Recalling that $\mathcal{C}^\theta_j$ is a preimage of $\mathcal{J}^\theta_{\zeta, \mp 1}$, we get
\begin{align*}%%\label{integral:mod-bessel-rational-zeta}
K^{(j)}_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
& = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right],
\end{align*}
where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $\mathcal{C}^\theta_j$, respectively. \begin{todo}[Draw the thimble in the $u$ plane?]\end{todo}

@@

\subsection{Specializing from the Airy--Lucas example}

@@

\begin{equation}\label{integral:mod-bessel-airy}

@@

@@

Through a similar calculation, we see that $\borel\big[ e^z z^{-1/2}\,\tilde{W}_{-1} \big]$ sums to
\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_{-1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big). \]
Looking back at Section~\ref{neg-root}, we recognize this as a scalar multiple of $v_{-1}$.
\end{revised}
%
\subsubsection{Thimble projection reasoning}\label{contour-argument-airy}
%
\begin{revised}
In Section~\ref{contour-argument-AL}, we specialized the reasoning behind Lemma~\ref{lem:thimble_proj_formula-proof} to the case of the Airy--Lucas functions. We now specialize even further, down to the case of the Airy function. Like in Section~\ref{contour-argument-AL}, we first recast integral~\eqref{integral:mod-bessel-airy} into the $\zeta$ plane by setting $-\zeta = 4u^3 - 3u$, which implies that $-d\zeta = 3(4u^2 - 1)\,du$. Recall from Section~\ref{sec:airy} that the integration contour $\mathcal{C}^\theta_1$ runs through the critical point $u = \tfrac{1}{2}$, with its direction determined by the parameter $\theta$. The critical point splits $\mathcal{C}^\theta_1$ into two pieces: the incoming branch, where the orientation of the thimble runs toward the critical point, and the outgoing branch, where the orientation points away. Recalling that $\mathcal{C}^\theta_1$ is a preimage of $\mathcal{J}^\theta_{\zeta,1}$, we get \begin{todo}[Check sign of first line]\end{todo}
\begin{verify}
\begin{align*}
K(z) & = \frac{3}{2 \sinh\big(\tfrac{1}{3}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
& = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right]
\end{align*}
\end{verify}
\begin{align*}
K(z) & = -i\sqrt{3} \int_{\mathcal{C}^\theta_1} \exp\left[z \left(4u^3 - 3u\right)\right]\,du \\
& = \frac{i}{\sqrt{3}} \left[ \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\,\frac{1}{4u_+^2 - 1}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\,\frac{1}{4u_-^2 - 1}\,d\zeta \right],
\end{align*}
where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $\mathcal{C}^\theta_j$, respectively. Recognizing $4u^3 - 3u$ as the Chebyshev polynomial $T_3(u)$, we introduce a new variable $\phi$ with $u = \cos(\phi)$ and $-\zeta = \cos(3\phi)$. On the $\phi$ plane, which is an infinite branched cover of the $u$ plane, we can lift $\mathcal{C}^\theta_1$ to the path $\tfrac{\pi}{3} + i\R$. The incoming and outgoing branches lift to $\tfrac{\pi}{3} - i[0, \infty)$ and $\tfrac{\pi}{3} + i[0, \infty)$, respectively. \begin{todo}[Draw the lifted thimble in the $\phi$ plane?]\end{todo}

@@

In the projected thimble integral
\[ K(z) = \frac{i}{\sqrt{3}} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\left[\frac{1}{4u_+^2 - 1} - \frac{1}{4u_-^2 - 1}\right]\,d\zeta, \]
we can now see the integrand as the variation of the function
\[ \frac{1}{4\cos(\phi)^2 - 1} = \frac{1}{2}\;{}_2F_1\left(\frac{2}{3},\;\frac{4}{3};\;\frac{3}{2};\frac{1}{2} - \frac{\zeta}{2}\right) + \frac{1}{6}\;{}_2F_1\left(\frac{2}{3},\;\frac{4}{3};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) \]
across the branch cut $\mathcal{J}^\theta_{\zeta,1}$. The first term is regular at $\zeta = 1$, so only the second term contributes to the jump. We can write the jump explicitly using identity~15.2.3 from \cite{dlmf}:
\[ K(z) = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{6},\;\frac{5}{6};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta. \]
Comparing this expression with the expression for $V_1$ in Section~\ref{pos-root}, we see that
\[ K(z) = \tfrac{i}{2}\laplace_{\zeta, 1} v_1. \]
\end{revised}
\begin{old}\par
We can also study the Airy-Lucas functions by applying the thimble projection formula to integral~\eqref{integral:mod-bessel-rational-AL}, specializing the reasoning behind Lemma~\ref{lem:thimble_proj_formula-proof}. We recast integral~\eqref{integral:mod-bessel-rational-AL} into the $\zeta$ plane by setting $-\zeta = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$. Recall from below equation~\eqref{integral:AL} that the integration contour $\mathcal{C}^\theta_j$ run through the critical point $u = \cos\big(\tfrac{j}{n}\pi\big)$, with its direction determined by the parameter $\theta$. The critical point splits $\mathcal{C}^\theta_j$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away. Recalling that $\mathcal{C}^\theta_j$ is a preimage of $\mathcal{J}^\theta_{\zeta, \mp 1}$, we get
\begin{align*}%%\label{integral:mod-bessel-rational-zeta}
K^{(j)}_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
& = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right]
\end{align*}
where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $\mathcal{C}^\theta_j$, respectively. \begin{todo}[Draw the thimble in the $u$ plane?]\end{todo}

@@

\begin{equation}%%\label{integral:mod-bessel}
